Counting trees with a grid

### 2024-07-04 Trees_grid.Rmd
Estimation of volume

>>>>

## The same thing with the total volume

```{r}
ci_boot_vol <- function(df_init, df_boot){
  # df: dataframe with 2*B columns and n rows

  ## 1st step: 1 estimation for each sample
  est_boot <- c()
  for (c in 1:B) {
    a <- mapply(circle3_vol, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
    est_boot <- append(est_boot, sum(a/p))
  }
  est_boot <- sort(est_boot)

  ## 3rd step: reverse percentile CI
  # Target: the initial sample alone
  a <- mapply(circle3_vol, df_init[, 1], df_init[, 2], MoreArgs = list(15, 9, 6))
  est_init <- sum(a/p) # Estimated total thus obtained from the initial sample
  cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : 
      [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
  return(c(est_init,lim_inf,lim_sup))
}
```

res <- ci_boot_vol(random_points,df_boot)

end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
```
